Program Mutation is Just Program Transformation: \\ A Universal Approach to Mutant Generation

### 2023-03-02 paper/main.tex
more text

Of course, simple string replacement is not general enough to handle
many interesting mutations.  Consider the classic case of statement
deletion, one of the most widely used and important mutation
operators.  What string can we replace with another string in order to
delete a statement in a C program?  We would need an ``operator'' for
each possible C statement.  However, if we allow the use of
\emph{regular expression match and replace pairs} in place of simple
strings, we can easily express this operator, with some precision:

@@

@@

>>>>

Of course, simple string replacement is not general enough to handle
many interesting mutations.  Consider the classic case of statement
deletion, one of the most widely used and important mutation
operators~\cite{deng2013empirical}.  What string can we replace with another string in order to
delete a statement in a C program?  We would need an ``operator'' for
each possible C statement.  However, if we allow the use of
\emph{regular expression match and replace pairs} in place of simple
strings, we can easily express this operator, with some precision:

@@

Using regular expressions to express mutants has many benefits.  While
much more expressive than simple string replacement, regular
expressions are familliar to most developers.  In principle,
development of complex regular expressions for operators can even be
performed by simply providing examples~\cite{bartoli2014automatic}  or
describing the operator in natural
language~\cite{zhong2018generating}.  Implementing a mutation
generation tool for a language by providing the equivalent of our
Python program above with a list of regular expression matches and
replacements is clearly much easier than writing a mutation tool from
scratch, and much easier to maintain and extend.

@@

\section{Implementation}
